GNSS-based displacement detection using Bayesian inference

### 2020-11-20 paper/manuscript.tex
add dis figs

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=8 cm]{v_simple_p_model_add_new_rule}
	\caption{Bayesian model for displacement detection with an additional prior.}
	\label{fig_v_simple_p_model_add_new_rule}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_tau_add_new_rule}
	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
	\label{fig_v_bd9_4_up_tau_add_new_rule}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_mu_add_new_rule}
	\caption{Histogram of posterior estimation of the mean in field experiment 2 with an additional prior.}
	\label{fig_v_bd9_4_up_mu_add_new_rule}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_sigma_add_new_rule}
	\caption{Histogram of posterior estimation of the observation noise in field experiment 2 with an additional prior.}
	\label{fig_v_bd9_4_up_sigma_add_new_rule}
\end{figure}
